---
title: "FLARe case-control analysis"
author: "Tom McGregor"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    code_folding: hide
    df_print: paged
    highlight: monochrome
    number_sections: no
    theme: paper
params:
  group_comparison:
    value: anx_cont
    choices:
      - anx_cont
      - anx.current_cont
      - anx.life_cont
      - anx.nodep_cont
      - general.anx_control
      - social.anx_control
      - panic.anx_control
      - gad.anx_gad.control
      - gad.life_gad.life.control
  drop_exclusions:
    value: TRUE
    choices:
      - TRUE
      - FALSE
  avoiders_only:
    value: FALSE
    choices:
      - TRUE
      - FALSE
  drop_incomplete:
    value: TRUE
    choices:
      - TRUE
      - FALSE
  drop_twins:
    value: FALSE
    choices:
      - TRUE
      - FALSE
  bar_diamonds:
    value: duits_subjective
    choices:
      - duits_subjective
      - duits_overall
      - main_overall
---
# Setup

## Steps

* Clear workspace
```{r Clear workspace, include=FALSE}
# clear workspace
# rm(list = ls())
```

* Load packages
```{r Load packages, include=FALSE}
# install pacman package manager if it isn't already installed
if(!require("pacman")){
  install.packages(
    "pacman", 
    dependencies = TRUE
  )
}

# load pacman (package manager to allow install/library in one go using pload)
library('pacman')

# install (if necessary) and load packages
p_load(
psych, 
arsenal, 
knitr, 
broom, 
gridExtra, 
corrr, 
Hmisc, 
effsize, 
extrafont, 
rlang, 
kableExtra, 
miceadds, 
gmodels, 
BayesFactor, 
data.table, 
patchwork, 
RPMG,
tidyverse,
gt,
DT,
janitor
  )
```

* Set seed
```{r Set seed, include=FALSE}
# set seed
knitr::opts_chunk$set(
  set.seed(31290)
)
```

* Save date
```{r Save date, include=FALSE}
# save date
date <- Sys.Date()
```

* Import objects created from cleaning script
```{r Import cleaning objects, include=FALSE}
# dataframe, variables of interest, trials
load("../data/df1.RData")
load("../data/vars_of_interest.RData")
load("../data/vars_of_interest_thirds.RData")
load("../data/fc_trials.RData")
load("../data/emailed_n.RData")
load("../data/consented_n.RData")
load("../data/passed_screening_n.RData")
load("../data/complete_n.RData")
load("../data/TEDS.RData")
```

* Create functions
```{r Create functions, echo=FALSE}
# standard error function
se_func <- function(x, na.rm=FALSE) {
  if (na.rm) x <- na.omit(x)
  sqrt(var(x)/length(x))
}

# 'not in' operator
'%!in%' <- function(x,y)!('%in%'(x,y))

# create a fuction to use when setting the breaks of the x axis in elephant plots. The function recognises whether the number of trials is more than 12, if it is it will give the x axis 18 points (i.e. extinction) and if it isn't it will give it 12 points (i.e. acquisition)
breaks_fun <- function(x) {
  if (max(x) > 12) {
    seq(0, 18, 1)
  } else {
    seq(0, 12, 1)
  }
}

# save table
save_table <- function(df) {
  table_name <- deparse(substitute(df))
  fwrite(
    df, 
    file = 
      paste0(
        "../results/", 
        group_comparison_char, 
        "/",
        table_name,
        "_",
        date,
        ".csv"
      )
  )
}

# save plot
save_plots <- function(plot) {
  plot_name <- deparse(substitute(plot))
  suppressMessages(
    ggsave(
      plot = plot, 
      file = 
        paste0(
          "../plots/", 
          group_comparison_char,
          "/",
          plot_name, 
          "_",
          date,
          ".pdf"
        )
    )
  )
}
```

* Set parameterized objects
```{r Parameterized objects, include=FALSE}
# symbol and character versions of parameters
group_comparison <- as.symbol(params$group_comparison)
group_comparison_char <- as.character(params$group_comparison)
bar_diamonds <- as.symbol(params$bar_diamonds)
```

* Comparison being made: **`r group_comparison_char`**

* Create folders
```{r Create folders, include=FALSE}
dir.create(
  path = 
    paste0(
      "../plots/",
      group_comparison_char
      ), 
  recursive = T, 
  showWarnings = F
)

dir.create(
  path = 
    paste0(
    "../results/", 
    group_comparison_char
  ), 
  recursive = T, 
  showWarnings = F
)
```

## Invited v. consented comparisons {.tabset .tabset-fade}
### Age
```{r Invited v consented age, echo=FALSE}
# ttest for difference in age between groups
invited_consented_age_ttest <- TEDS %>% 
  t.test(
    CurrentAge ~ did_consent_factor, data = .
  )

invited_consented_age_cohend <- TEDS %>%
  cohen.d(
    CurrentAge ~ did_consent_factor, data = .
  )
```

d = `r round(invited_consented_age_cohend$estimate, 2)`; t(`r round(invited_consented_age_ttest$parameter, 2)`) = `r round(invited_consented_age_ttest$statistic, 2)`, p = `r round(invited_consented_age_ttest$p.value, 3)`.

### Gender
```{r Invited v consented gender, echo=FALSE}
# chi-square test for gender
# create a contingency table for sex by grouping variable
invited_consented_gender_table <- TEDS %>% 
  select(did_consent_factor, Sex) %>% 
  table()

invited_consented_gender_chisq <- stats::chisq.test(invited_consented_gender_table)
invited_consented_gender_fisher <- stats::fisher.test(invited_consented_gender_table)
```

OR = `r round(invited_consented_gender_fisher$estimate, 2)`; 95% CI = `r round(invited_consented_gender_fisher$conf.int[1], 2)`, `r round(invited_consented_gender_fisher$conf.int[2], 2)`, p < `r round(invited_consented_gender_chisq$p.value, 3)`

## Exclusion drop

Exclusions for task avoidance: restarts/volume/headphones/instructions.

Number of participants before exclusion drop: **`r nrow(df1)`**.  
  
```{r GAD excluded v completers, echo=F, fig.align='left'}
df1 %>% 
  group_by(exclude) %>%
  summarise(
    count = n(),
    meanGAD = round(mean(GAD, na.rm = T), 2),
    seGAD = round(se_func(GAD, na.rm = T), 2)
  ) %>% 
  mutate(
    mean_se = paste0(meanGAD, " ", "(", seGAD, ")"),
    exclude = paste0(exclude, " ", "(n = ", count, ")")
  ) %>% 
  select(Exclude = exclude, `GAD-7 M (SE)` = mean_se) %>%
  kable(align = c('l', 'r'))

exclude_gad_ttest <- df1 %>% 
  t.test(
    GAD ~ exclude, data = .
  )

exclude_gad_cohend <- df1 %>% 
  cohen.d(
    GAD ~ exclude, data = .
  )
```
<br>GAD-7 difference between included and excluded participants: **d = `r round(exclude_gad_cohend$estimate, 2)`; t(`r round(exclude_gad_ttest$parameter, 2)`) = `r round(exclude_gad_ttest$statistic, 2)`, p = `r round(exclude_gad_ttest$p.value, 3)`.**

Dropping exclusions? **`r params$drop_exclusions`**.

```{r Exclusion drop, include=FALSE}
if(params$drop_exclusions){
  df1 <- df1 %>% 
    filter(
      exclude == "no"
    )
}

not_excluded_n <- nrow(df1)
```

Number of participants after drop (if applicable): **`r nrow(df1)`**.
  
## Task avoiders only 

***Exclusion drop must equal FALSE***

Task avoidance: restarts/volume/headphones/instructions.

Number of participants before non-avoiders dropped: **`r nrow(df1)`**.

Dropping non-avoiders? **`r params$avoiders_only`**. 

```{r Exclusions only, include=FALSE}
if(params$avoiders_only){
  df1 <- df1 %>% 
    filter(
      exclude == "yes"
    )
}
```

Number of participants after drop (if applicable): **`r nrow(df1)`**.

## Incomplete cases check

Number of participants incomplete cases drop: **`r nrow(df1)`**.

Dropping incomplete cases? **`r params$drop_incomplete`**.
```{r Incomplete cases check, include=FALSE}
if(params$drop_incomplete){
  df1 <- df1 %>%
    # remove rows with missing data for key variables
    filter(
      complete.cases(
        FCT1CSpMea, 
        FCT1CSmMea, 
        FCT1CSdifMea, 
        FCT3CSpMea, 
        FCT3CSmMea, 
        FCT3CSdifMea
      )
    )
}

without_missing_data_n <- nrow(df1)
```

Number of participants after drop (if applicable): **`r nrow(df1)`**.
  
## Twin check

Number of participants pre twin drop: **`r nrow(df1)`**.

Dropping twins? **`r params$drop_twins`**.
```{r Twin check, include=FALSE}
if(params$drop_twins){
  df1 <- df1 %>% 
    group_by(FamilyID) %>%
    sample_n(1) %>% 
    ungroup()
}
```

Number of participants after drop (if applicable): **`r nrow(df1)`**.
  
## Participant breakdown
Number of participants emailed: **`r emailed_n`**

Number of participants consented: **`r consented_n`**

Number of participants who passed screening: **`r passed_screening_n`**

Number of participants who completed the study: **`r complete_n`**

Number of participants who weren't excluded: **`r not_excluded_n`**

Number of participants without missing data: **`r without_missing_data_n`**

***

# Phenotypic check {.tabset .tabset-fade}

## Group numbers
Number of participants in each group.

```{r Check numbers in each group, echo=FALSE}
group_check <- df1 %>% 
  mutate(
    {{group_comparison}} :=
      fct_explicit_na(
        factor({{group_comparison}}),
        na_level = "missing"
        )
  ) %>% 
  group_by({{group_comparison}}) %>% 
  count() %>% 
  rename(group = {{group_comparison}})

save_table(group_check)

group_check %>% 
kable()
```
<br>Wide and long dataframes are created from cases and controls.

Participants who are missing for the grouping variable are removed.

```{r Create df, include=FALSE}
# new (better) names for vars_of_interest
newnames  <-  vars_of_interest %>% 
  str_replace_all(., "FCT1", "Acquisition_") %>% 
  str_replace_all(., "FCT3", "Extinction_") %>% 
  str_replace_all(., "Mea", "") %>% 
  str_replace_all(., "p", "+") %>% 
  str_replace_all(., "m", "-") %>% 
  str_replace_all(., "CSdif", "Discrimination")

# create wide df
df.wide <- df1 %>%
  filter(complete.cases({{group_comparison}}))
 

# create long df for variables of interest and status
df.long <- df.wide %>% 
  select({{group_comparison_char}}, vars_of_interest, FamilyID) %>% 
  gather("key", "score", -c({{group_comparison}}, FamilyID)) %>%
  mutate(
    measure = factor(ifelse(str_detect(key, "FCT"), "Expectancy", NA)),
    phase = factor(ifelse(str_detect(key, "FCT1"), "Acquisition", "Extinction")),
    stimulus = factor(
      case_when(str_detect(key, "CSp") ~ "CS+",
                str_detect(key, "CSm") ~ "CS-",
                str_detect(key, "dif") ~ "Discrimination",
                str_detect(key, "Dif") ~ "Discrimination"),
      levels = c("CS+", "CS-", "Discrimination"))) %>% 
  mutate({{group_comparison_char}} := factor({{group_comparison}})) %>% 
  select(FamilyID, {{group_comparison_char}}, measure, phase, stimulus, score)

# Save data sets for df.wide and df.long (for main analysis only)
if(group_comparison_char == "anx_cont"){
  write.csv(df.wide, paste0("../data/study1-dataset-wide", "-", date, ".csv"))
  write.csv(df.long, paste0("../data/study1-dataset-long", "-", date, ".csv"))
}
```

## Sample table
```{r Sample table, echo=FALSE}
# create sample table giving descriptive statistics for each group (i.e. cases and controls)
sample_table <- df.wide %>% 
  group_by({{group_comparison}}) %>% 
  summarise(
    
    count = n(),
    
    nFemale = sum(Sex == "female"),
    propFemale = mean(Sex == "female"),
    nMale = sum(Sex == "male"),
    propMale = mean(Sex == "male"),
    
    meanAge = mean(CurrentAge),
    seAge = se_func(CurrentAge, na.rm = T),
    meanGAD = mean(GAD),
    seGAD = se_func(GAD, na.rm = T),
    
    nLifetime = sum(GAD.dia == 0 & MHQ.Anx == 1),
    nCurrent = sum(GAD.dia == 1 & MHQ.Anx == 0),
    nLifeAndCurrent = sum(GAD.dia == 1 & MHQ.Anx == 1)
  ) %>% 
  mutate_if(is.numeric, ~round(., 2)) %>% 
  mutate(
    group = case_when(
      {{group_comparison}} == "case" ~ paste0("Anxious", " ", "(N = ", count, ")"),
      {{group_comparison}} == "control" ~ paste0("Non-anxious", " ", "(N = ", count, ")")
    ),
    Females = paste0(nFemale, " ", "(", propFemale, ")"),
    Males = paste0(nMale, " ", "(", propMale, ")"),
    Age = paste0(meanAge, " ", "(", seAge, ")"),
    `GAD-7` = paste0(meanGAD, " ", "(", seGAD, ")")
  ) %>% 
  select(
    group,
    Females,
    Males,
    Age,
    `GAD-7`,
    `Self-reported lifetime diagnosis` = nLifetime,
    `GAD-7 diagnosis` = nCurrent,
    `Self-reported lifetime diagnosis & GAD-7 diagnosis` = nLifeAndCurrent
  ) %>% 
  gather(measure, value, -group) %>%
  mutate(measure = factor(measure, 
                          levels = c(
                            "group",
                            "Females",
                            "Males",
                            "Age",
                            "GAD-7",
                            "Self-reported lifetime diagnosis",
                            "GAD-7 diagnosis",
                            "Self-reported lifetime diagnosis & GAD-7 diagnosis"
                          ))) %>% 
  spread(group, value) %>% 
  mutate(measure_group = case_when(
    measure == "Females"|measure == "Males" ~ "Sex (%)",
    measure == "Age"|measure == "GAD-7" ~ "Group means (SE)",
    TRUE ~ "Number of participants meeting criteria for one or both grouping conditions"
  )
  ) %>% 
  select(measure_group, everything())

save_table(sample_table)

sample_table %>% 
  gt(rowname_col = "measure", groupname_col = "measure_group") %>%
  tab_header(title = "Sample table")
```

## Anxiety breakdown

```{r Anxiety breakdown, echo=FALSE}
anxiety_breakdown <- df.wide %>%
  filter({{group_comparison}} == "case") %>%
  mutate_at(c("MHQ.AnxGen", "MHQ.AnxPA", "MHQ.AnxSoc", "MHQ.AnxAgo", "MHQ.OCD", "MHQ.OCDoth", "MHQ.PTSD", "MHQ.AnxPho"), ~replace_na(., replace = 0)) %>% 
  select(MHQ.AnxGen, MHQ.AnxPA, MHQ.AnxSoc, MHQ.AnxAgo, MHQ.OCD, MHQ.OCDoth, MHQ.PTSD, MHQ.AnxPho) %>% 
  group_by(MHQ.AnxGen, MHQ.AnxPA, MHQ.AnxSoc, MHQ.AnxAgo, MHQ.OCD, MHQ.OCDoth, MHQ.PTSD, MHQ.AnxPho) %>% 
  count() %>% 
  mutate(Diagnosis = case_when(
    sum(MHQ.AnxGen, MHQ.AnxPA, MHQ.AnxSoc, MHQ.AnxAgo, MHQ.OCD, MHQ.OCDoth, MHQ.PTSD, MHQ.AnxPho) == 0 ~ "GAD-7 diagnosis",
    
    MHQ.AnxGen == 1 & sum(MHQ.AnxPA, MHQ.AnxSoc, MHQ.AnxAgo, MHQ.OCD, MHQ.OCDoth, MHQ.PTSD, MHQ.AnxPho) == 0 ~ "Generalised anxiety",
    MHQ.AnxPA == 1 & sum(MHQ.AnxGen, MHQ.AnxSoc, MHQ.AnxAgo, MHQ.OCD, MHQ.OCDoth, MHQ.PTSD, MHQ.AnxPho) == 0 ~ "Panic attacks",
    MHQ.AnxSoc == 1 & sum(MHQ.AnxGen, MHQ.AnxPA, MHQ.AnxAgo, MHQ.OCD, MHQ.OCDoth, MHQ.PTSD, MHQ.AnxPho) == 0 ~ "Social phobia",
    MHQ.AnxAgo == 1 & sum(MHQ.AnxGen, MHQ.AnxPA, MHQ.AnxSoc, MHQ.OCD, MHQ.OCDoth, MHQ.PTSD, MHQ.AnxPho) == 0 ~ "Agoraphobia",
    
    MHQ.AnxGen == 1 & MHQ.AnxPA == 1 & sum(MHQ.AnxSoc, MHQ.AnxAgo, MHQ.OCD, MHQ.OCDoth, MHQ.PTSD, MHQ.AnxPho) == 0 ~ "Generalised anxiety & panic attacks",
    MHQ.AnxGen == 1 & MHQ.AnxSoc == 1 & sum(MHQ.AnxPA, MHQ.AnxAgo, MHQ.OCD, MHQ.OCDoth, MHQ.PTSD, MHQ.AnxPho) == 0 ~ "Generalised anxiety & social phobia",
    MHQ.AnxGen == 1 & MHQ.AnxAgo == 1 & sum(MHQ.AnxPA, MHQ.AnxSoc, MHQ.OCD, MHQ.OCDoth, MHQ.PTSD, MHQ.AnxPho) == 0 ~ "Generalised anxiety & agoraphobia",
    
    MHQ.AnxSoc == 1 & MHQ.AnxPA == 1 & sum(MHQ.AnxGen, MHQ.AnxAgo, MHQ.OCD, MHQ.OCDoth, MHQ.PTSD, MHQ.AnxPho) == 0 ~ "Social phobia & panic attacks",
     MHQ.AnxSoc == 1 & MHQ.AnxAgo == 1 & sum(MHQ.AnxGen, MHQ.AnxPA, MHQ.OCD, MHQ.OCDoth, MHQ.PTSD, MHQ.AnxPho) == 0 ~ "Social phobia & agoraphobia",
    
    MHQ.AnxAgo == 1 & MHQ.AnxPA == 1 & sum(MHQ.AnxGen, MHQ.AnxSoc, MHQ.OCD, MHQ.OCDoth, MHQ.PTSD, MHQ.AnxPho) == 0 ~ "Agoraphobia & panic attacks",
    
    sum(MHQ.AnxGen, MHQ.AnxPA, MHQ.AnxSoc, MHQ.AnxAgo, MHQ.OCD, MHQ.OCDoth, MHQ.PTSD, MHQ.AnxPho) >= 3 ~ "Three or more diagnoses",
    
    TRUE ~ "Undefined"
  )
  ) %>% 
  ungroup() %>% 
  select(Diagnosis, n) %>% 
  filter(Diagnosis != "GAD-7 diagnosis") %>% 
  group_by(Diagnosis) %>% 
  summarise(`N` = sum(n)) %>% 
  arrange(Diagnosis)

save_table(anxiety_breakdown)

anxiety_breakdown %>% 
  gt(rowname_col = "Diagnosis") %>%
  tab_header(title = "Breakdown of self-reported, clinician-provided, diagnoses of anxiety disorders")
```

## Twin breakdown

```{r Twin breakdown,echo=FALSE}
concordant_twins <- df.wide %>% 
  group_by({{group_comparison}}, FamilyID, Zygosity) %>%
  count() %>% 
  ungroup() %>% 
  group_by({{group_comparison}}, Zygosity, n) %>% 
  count() %>% 
  ungroup() %>% 
  filter(n == 2) %>% 
  select({{group_comparison}}, Zygosity, n = nn) %>% 
  mutate(concordance = "concordant")

concordant_twins_by_zygosity <- concordant_twins %>% 
  group_by(Zygosity) %>% 
  summarise(concordant_twin_pairs = sum(n))

discordant_twins <- df.wide %>% 
  group_by(FamilyID, Zygosity) %>% 
  count() %>%
  ungroup() %>% 
  group_by(Zygosity, n) %>% 
  count() %>% 
  ungroup() %>% 
  filter(n == 2) %>% 
  select(Zygosity, total_twin_pairs = nn) %>% 
  right_join(concordant_twins_by_zygosity, by = "Zygosity") %>% 
  mutate(
    discordant_twin_pairs = total_twin_pairs - concordant_twin_pairs,
    concordance = "discordant",
    {{group_comparison}} := "cross-group"
  ) %>% 
  select({{group_comparison}}, Zygosity, n = discordant_twin_pairs, concordance)

singletons <- df.wide %>% 
  group_by(FamilyID) %>% 
  mutate(pair = n()>1) %>% 
  ungroup() %>% 
  filter(pair == FALSE) %>% 
  group_by({{group_comparison}}, Zygosity) %>% 
  count() %>%
  mutate(concordance = "singletons")

twin_split <- bind_rows(
  concordant_twins, 
  discordant_twins, 
  singletons
) %>% 
  select(concordance, {{group_comparison}}, Zygosity, n) %>% 
  spread(Zygosity, n) %>% 
  rename(MZ = "1", DZ = "2") %>% 
  mutate(
    MZ = ifelse(
      concordance == "singletons", MZ, 2*(MZ)
    ),
    DZ = ifelse(
      concordance == "singletons", DZ, 2*(DZ)
    ),
    n = MZ + DZ,
    pairs = ifelse(
      concordance == "singletons", NA_real_, n/2
    ),
    mz_percent = MZ/n
    ) %>% 
  add_row(concordance = " ", 
          {{group_comparison}} := "Total",
          MZ = sum(.$MZ),
          DZ = sum(.$DZ),
          n = sum(.$n),
          pairs = sum(.$pairs, na.rm = T),
          mz_percent = MZ/n
  ) %>% 
  mutate_if(is.double, ~round(., 2))

save_table(twin_split)

twin_split_gt <- twin_split %>%
  select(concordance, {{group_comparison}}, "Individual twins" = n, "Twin pairs" = pairs, "%MZ" = mz_percent) %>% 
  mutate(
    concordance = str_to_title(concordance),
    {{group_comparison}} := recode(
      {{group_comparison}},
      case = "Anxious", 
      control = "Non-anxious",
      'cross-group' = "Cross-group"
    )
  ) %>% 
  gt(rowname_col = {{group_comparison_char}}, groupname_col = "concordance") %>%
  tab_header(
    title = "Twin breakdown",
    subtitle = "Individuals, pairs and %MZ broken down across groups"
  ) %>%
  fmt_percent(columns = vars('%MZ'), decimals = 0) %>%
  fmt_missing(columns = vars("Twin pairs"), missing_text = "---")

twin_split_gt
```

## Age

**Case v control comparison**
```{r Case v control age, echo=FALSE}
# ttest for difference in age between groups
case_control_age_ttest <- df.wide %>% 
  t.test(
    CurrentAge ~ get(group_comparison_char), data = .
  )

case_control_age_cohend <- df.wide %>% 
  cohen.d(
    CurrentAge ~ get(group_comparison_char), data = .
  )
```

d = `r round(case_control_age_cohend$estimate, 2)`; t(`r round(case_control_age_ttest$parameter, 2)`) = `r round(case_control_age_ttest$statistic, 2)`, p = `r round(case_control_age_ttest$p.value, 3)`.

## Gender

**Case v control comparison**
```{r Case v control gender, echo=FALSE}
# chi-square test for gender
# create a contingency table for sex by grouping variable
group_gender_table <- df.wide %>% select(Sex, {{group_comparison}}) %>% table()

group_gender_chisq <- stats::chisq.test(group_gender_table)
group_gender_fisher <- stats::fisher.test(group_gender_table)
```

OR = `r round(group_gender_fisher$estimate, 2)`; 95% CI = `r round(group_gender_fisher$conf.int[1], 2)`, `r round(group_gender_fisher$conf.int[2], 2)`, p < `r round(group_gender_chisq$p.value, 3)`

## GAD & PHQ {.tabset .tabset-fade}

### Correlations
```{r GAD PHQ correlation, include=FALSE}
# Create correlation matrix
correlation <- df.wide %>% 
  select(GAD, PHQ, vars_of_interest) %>% 
  as.matrix() %>%
  rcorr(type = "spearman")
```

Correlation between GAD and PHQ: `r round(correlation$r["GAD","PHQ"], 2)`, p = `r round(correlation$P["GAD","PHQ"], 3)`

```{r GAD PHQ correlation with vars of interest, echo=FALSE}
# GAD and PHQ correlation with vars of interest
df.wide %>% 
  select(GAD, PHQ, vars_of_interest) %>%
  rename_at(vars(vars_of_interest), ~ newnames) %>% 
  correlate(quiet = T) %>% 
  # focus tidies the correlation matrix
  focus(GAD, PHQ) %>% 
  rename(Measure = rowname) %>% 
  mutate_if(is.double, ~round(., 2)) %>%
  kable()
```

### T-tests {.tabset .tabset-fade}

**GAD-7: case v control**
```{r GAD t test, echo=FALSE}
# ttest for difference in GAD between groups
group_gad_ttest <- df.wide %>% 
  t.test(
    GAD ~ get(group_comparison_char), data = .
  )

group_gad_cohend <- df.wide %>% 
  cohen.d(
    GAD ~ get(group_comparison_char), data = .
  )
```
d = `r round(group_gad_cohend$estimate, 2)`; t(`r round(group_gad_ttest$parameter, 2)`) = `r round(group_gad_ttest$statistic, 2)`, p = `r round(group_gad_ttest$p.value, 3)`.

**PHQ: case v control**
```{r PHQ t test, echo=FALSE}
# ttest for difference in PHQ between groups
group_phq_ttest <- df.wide %>% 
  t.test(
    PHQ ~ get(group_comparison_char), data = .
  )

group_phq_cohend <- df.wide %>% 
  cohen.d(
    PHQ ~ get(group_comparison_char), data = .
  )
```

d = `r round(group_phq_cohend$estimate, 2)`; t(`r round(group_phq_ttest$parameter, 2)`) = `r round(group_phq_ttest$statistic, 2)`, p = `r round(group_phq_ttest$p.value, 3)`.

***

# Expectancies {.tabset .tabset-fade}
## Expectancy summary
```{r Summary table, echo=FALSE}
# expectancy_summary: n, missing, min, max, mean, median, sd, se, ci, skew, kurtosis
expectancy_summary <- df.wide %>%
  rename_at(vars(vars_of_interest), ~ newnames) %>% 
  select({{group_comparison}}, tidyselect::all_of(newnames)) %>%
  group_by({{group_comparison}}) %>%
  summarise_all(
    list( 
      ~ n(),
      missing = ~sum(is.na(.)),
      ~min(.),
      ~max(.),
      ~mean(.), 
      ~median(.),
      ~sd(x = .), 
      se = ~se_func(.),
      ~skew(.), 
      kurtosis = ~kurtosi(.))
  ) %>% 
  ungroup() %>% 
  gather(var, value, -{{group_comparison}}) %>%
  separate(var, c("phase", "stimulus", "measure"), "_", extra = "drop") %>% 
   mutate(
    stimulus = factor(
      stimulus, 
      levels = c(
        "CS+", 
        "CS-", 
        "Discrimination"
      )
    )
  ) %>% 
  spread(measure, value) %>% 
  mutate(
    lower_ci = mean - qt(1 - (0.05 / 2), n - 1) * se,
    upper_ci = mean + qt(1 - (0.05 / 2), n - 1) * se
  ) %>%
  mutate_if(is.numeric, round, 2) %>%
  gather(measure, value, -c({{group_comparison}}, phase, stimulus)) %>% 
  spread({{group_comparison}}, value) %>% 
  mutate(
    measure = factor(
      measure, 
      levels = c(
        "n", 
        "missing", 
        "min", 
        "max", 
        "mean", 
        "median", 
        "sd", 
        "se", 
        "lower_ci",
        "upper_ci",
        "skew", 
        "kurtosis"
      )
    )
  ) %>% 
  arrange(phase, stimulus, measure)

save_table(expectancy_summary)

datatable(expectancy_summary)
```

## Interaction plot
```{r Interaction plot, echo=F}
# Interaction plot
interaction_plot <- expectancy_summary %>% 
  filter(stimulus != "Discrimination") %>%
  gather({{group_comparison_char}}, "value", c("case", "control")) %>% 
  spread(measure, value) %>% 
  ggplot(aes(x = stimulus, y = mean, colour = {{group_comparison}})) + 
  geom_point() +
  geom_line(aes(group = {{group_comparison}})) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = .3) +
  facet_wrap(~phase)

save_plots(interaction_plot)

interaction_plot
```

## Distributions 1: Scatterplots with boxplot overlays
```{r Scatterplots with boxplot overlays, echo=FALSE}
# Scatterplot with boxplot overlay to highlight outliers for each stimulus per condition
scatterplot <- df.long %>%
  ggplot(
    ., 
    aes(
      x = fct_rev(stimulus:{{group_comparison}}), 
      y = score, 
      color = stimulus
    )
  ) +
  geom_point(position = "jitter", alpha = .5) +
  geom_boxplot(
    aes(group = stimulus:{{group_comparison}}), 
    color = "black", 
    alpha = 0, 
    width = .5
  ) +
  facet_wrap(~ phase) +
  coord_flip() +
  theme(panel.background = element_blank()) +
  scale_colour_manual(values = c("#F5434A", "#14A8EC", "#EF42DF")) +
  labs(title = paste(group_comparison_char), keep = T)

save_plots(scatterplot)

scatterplot
```

## Distributions 2: Density plots for each stimulus per condition
```{r Density plots for each stimulus per condition, echo=FALSE}
# Density plots for each stimulus per condition
density_plot <- df.long %>%
  ggplot(
    .,
    aes(
      x = score, 
      colour = {{group_comparison}},
      fill = {{group_comparison}}, 
      alpha = .8
    )
  ) +
  geom_density(position = "identity") +
  facet_wrap(
    phase ~ stimulus, 
    nrow = length(unique(df.long$phase)), 
    ncol = length(unique(df.long$stimulus))
  ) + 
  scale_color_manual(values=c("#00AFBB", "#FF0066", "orange")) +
  scale_fill_manual(values=c("#00AFBB", "#FF0066", "orange")) +
  theme(panel.background = element_blank()) +
  labs(title = paste(group_comparison_char), keep = T)

save_plots(density_plot)

density_plot
```

***

# Fear conditioning analyses {.tabset .tabset-fade}

## Means {.tabset .tabset-fade}

### ANOVAs
```{r anova of means for both phases, echo=FALSE}
# run anova for both phases - means
means_aov <- df.long %>% 
  # remove Discrimination rows
  filter(stimulus != "Discrimination") %>%
  # group by phase (acquisition/extinction)
  group_by(phase) %>%
  # nest the df - essentially create a df for each grouping set above 
  nest() %>% 
  # create new list columns in the df containing anova model output and tidied version of the model output
  mutate(model = map(data, ~aov(score ~ get(group_comparison_char) * stimulus, data = .)),
         tidy = map(model, broom::tidy)) %>% 
  select(phase, tidy) %>% 
  # unnest the tidy df
  unnest(tidy) %>% 
  ungroup() %>% 
  # arrange output based on measure and phase groupings
  arrange(phase) %>% 
  mutate_if(
    is.numeric,
    round,
    3
  )
  
datatable(means_aov)

save_table(means_aov)
```

### Follow-up tests
```{r Tukey tests for means for both phases, echo=FALSE}
# call and tidy the tukey posthoc
means_aov_tukey <- df.long %>% 
  # remove Discrimination rows
  filter(stimulus != "Discrimination") %>% 
  # group by phase (acquisition/extinction)
  group_by(phase) %>%
  # nest the df - essentially create a df for each grouping set above 
  nest() %>% 
  # create new list columns in the df containing anova model output, tukey follow-up tests and tidied version of the tukey follow-up tests
  mutate(model = map(data, ~aov(score ~ get(group_comparison_char) * stimulus, data = .)),
         tukey = map(model, TukeyHSD),
         tidy = map(tukey, broom::tidy)) %>% 
  select(phase, tidy) %>% 
  # unnest the tidy df
  unnest(tidy) %>% 
  ungroup() %>% 
  # arrange output based on measure and phase groupings
  arrange(phase) %>% 
  mutate_if(
    is.numeric,
    round,
    3
  )

datatable(means_aov_tukey)

save_table(means_aov_tukey)
```

### Intercepts
```{r Mean ANOVA intercepts, echo=FALSE}
mean_aov_intercepts <- df.long %>% 
  filter(stimulus != "Discrimination") %>% 
  group_by(phase) %>%
  group_map(
    ~aov(score ~ get(group_comparison_char) * stimulus, data = .) %>% 
      summary.aov(., intercept = T)
  ) 

mean_aov_intercepts
```

## Discriminations {.tabset .tabset-fade}

### ANOVAs
```{r anova of Discriminations for both phases, echo=FALSE}
# run anova for both phases - Discriminations by group
Discriminations_aov <- df.long %>% 
  filter(stimulus == "Discrimination") %>% 
  group_by(phase) %>%
  nest() %>% 
  mutate(model = map(data, ~aov(score ~ get(group_comparison_char), data = .)),
         tidy = map(model, broom::tidy)) %>% 
  select(phase, tidy) %>% 
  unnest(tidy) %>% 
  ungroup() %>% 
  arrange(phase) %>% 
  mutate_if(
    is.numeric,
    round,
    3
  )

datatable(Discriminations_aov)

save_table(Discriminations_aov)
```

### Follow-up tests
```{r Tukey tests for Discriminations for both phases, echo=FALSE}

# call and tidy the tukey posthoc
Discriminations_aov_tukey <- df.long %>% 
  filter(stimulus == "Discrimination") %>% 
  group_by(phase) %>%
  nest() %>% 
  mutate(model = map(data, ~aov(score ~ get(group_comparison_char), data = .)),
         tukey = map(model, TukeyHSD),
         tidy = map(tukey, broom::tidy)) %>% 
  select(phase, tidy) %>% 
  unnest(tidy) %>%
  ungroup() %>% 
  arrange(phase) %>% 
  mutate_if(
    is.numeric,
    round,
    3
  )

datatable(Discriminations_aov_tukey)

save_table(Discriminations_aov_tukey)
```

### Intercepts
```{r Discrimination ANOVA intercepts, echo=FALSE}
Discriminations_aov_intercepts <- df.long %>% 
  filter(stimulus == "Discrimination") %>% 
  group_by(phase) %>%
  group_map(
    ~aov(score ~ get(group_comparison_char), data = .) %>% 
      summary.aov(., intercept = T)
  )

Discriminations_aov_intercepts
```

## Expectancy means table
```{r sig dif df creation, include=FALSE}
# create df to combine p values for all comparisons between cases and controls on FC measures

sig_difs <- bind_rows(
  # combine rows from the tukey comparisons
  means_aov_tukey,
  Discriminations_aov_tukey,
  .id = "key") %>% 
  # convert to dataframe
  as_data_frame(.) %>% 
  # recode the values in the key column to reflect the dfs they came from
  mutate(key = recode_factor(
    key,
    '1' = "Means",
    '2' = "Discriminations"
  )) %>%
  # remove rows that compare across different types of stimuli
  filter(comparison %in% c("control:CS+-case:CS+", "control:CS--case:CS-", "control-case")) %>% 
  # select columns of interest
  select(key, phase, comparison, adj.p.value) %>% 
  # create stimulus column by detecting presence of stimulus in other columns
  mutate(Stimulus =
  case_when(
    key == "Discriminations" ~ "Discrimination",
    str_detect(comparison, "CS\\+") ~ "CS+",
    str_detect(comparison, "CS\\-") ~ "CS-"
    )) %>%
  filter((key == "Means" & comparison != "control-case")|key == "Discriminations") %>% 
  # remove unwanted columns and capitalise columns
  select(Phase = phase, Stimulus, Adj.p.value = adj.p.value) %>% 
  # convert all character columns to factors
  mutate_if(is.character, ~ as.factor(.)) %>% 
  # reorder the levels of the factors to match other dfs
  mutate(
    Stimulus = fct_relevel(Stimulus, "CS+")
  ) %>% 
  arrange(Phase, Stimulus)
```

```{r df of cohens d values, include = FALSE}
## Cohen's d
### Create df of Cohen's d values for each phase and stimulus

# set objects that specify levels of the columns that are going to be looped through
phase<-levels(df.long$phase)
stimulus<-levels(df.long$stimulus)

# create an empty dataframe
df_cohensd_results<-NULL

# for loop that goes through every combination of phase, measure and stimulus
for(phase_i in phase){
    for(stimulus_i in stimulus){
      
      # save a temporary subset of the dataframe for the current phase, measure, stimulus combination
      df.long.tmp<-df.long[  df.long$phase == phase_i &
                               df.long$stimulus == stimulus_i,]
      
      # save a temporary output of the cohen's d output for the current phase, measure, stimulus combination
      d_out_tmp<-cohen.d(score ~ get(group_comparison_char), data = df.long.tmp)
      
      # create a temporary dataframe of the columns of interest
      results_tmp<-data.frame( Phase = phase_i,
                               Stimulus = stimulus_i,
                               Estimate = d_out_tmp$estimate,
                               Conf.int.lower = d_out_tmp$conf.int[1],
                               Conf.int.upper = d_out_tmp$conf.int[2], 
                               row.names=NULL)
      
      # add the temporary dataframe (containing a row of the variables of interest for the current phase, measure, stimulus combination) to the empty dataframe 'df_cohensd_results'
      df_cohensd_results<-rbind(df_cohensd_results, results_tmp)
    }
}
```

```{r cohens d values with sig, echo = FALSE}
# create df of all the cohens d scores and their significance levels and duits' estimates as a reference 
df_cohensd <- df_cohensd_results %>% 
  # rearrange data in the same order as column ordering 
  arrange(Phase, Stimulus) %>%
  # add p values from existing df
  left_join(sig_difs, by = c("Phase", "Stimulus")) %>% 
  
  # create new columns
  mutate(
  # duits' effect sizes
    # duits' subjective rating values
    duits_subjective = case_when(
      Phase == "Acquisition" & Stimulus == "CS+" ~ -.04,
      Phase == "Acquisition" & Stimulus == "CS-" ~ .34,
      Phase == "Acquisition" & Stimulus == "Discrimination" ~ -.45,
      Phase == "Extinction" & Stimulus == "CS+" ~ .38,
      Phase == "Extinction" & Stimulus == "CS-" ~ .26,
      Phase == "Extinction" & Stimulus == "Discrimination" ~ .12),
    # duits' overall values
    duits_overall = case_when(
      Phase == "Acquisition" & Stimulus == "CS+" ~ -.067,
      Phase == "Acquisition" & Stimulus == "CS-" ~ .296,
      Phase == "Acquisition" & Stimulus == "Discrimination" ~ -.1541,
      Phase == "Extinction" & Stimulus == "CS+" ~ .352,
      Phase == "Extinction" & Stimulus == "CS-" ~ .126,
      Phase == "Extinction" & Stimulus == "Discrimination" ~ .147),
    
    # main overall findings
    main_overall = case_when(
      Phase == "Acquisition" & Stimulus == "CS+" ~ -.15,
      Phase == "Acquisition" & Stimulus == "CS-" ~ .28,
      Phase == "Acquisition" & Stimulus == "Discrimination" ~ -.25,
      Phase == "Extinction" & Stimulus == "CS+" ~ .33,
      Phase == "Extinction" & Stimulus == "CS-" ~ .25,
      Phase == "Extinction" & Stimulus == "Discrimination" ~ .13),
    
  # significance levels
    # below .001
    sig_001 = ifelse(Adj.p.value <.001 , Estimate, NA),
    # below .01
    sig_01 = ifelse(Adj.p.value <.01 & Adj.p.value >=.001, Estimate, NA),
    # below .01
    sig_05 = ifelse(Adj.p.value <.05 & Adj.p.value >=.01, Estimate, NA),
    
  # nudging levels  
    # sig 001 nudging for y
    ynudge_001 = ifelse(
                sig_001 >= 0, 
                Conf.int.upper + .03,
                Conf.int.lower - .03),
    # sig 01 nudging for y
    ynudge_01 = ifelse(
                sig_01 >= 0, 
                Conf.int.upper + .03,
                Conf.int.lower - .03),
    # sig 05 nudging for y
    ynudge_05 = ifelse(
                sig_05 >= 0, 
                Conf.int.upper + .03,
                Conf.int.lower - .03)
      ) %>% 
  mutate_if(is.logical, as.numeric) %>% 
    mutate_if(
      is.numeric,
      round,
      3
      )
```

```{r Expectancy means, echo=F}
expectancy_means <- expectancy_summary %>% 
  filter(measure == "mean"| measure == "se"| measure == "n") %>% 
  gather(key, value, c(case, control)) %>% 
  spread(measure, value) %>% 
  mutate(
    mean_se = paste0(mean, " (", se, ")"),
    key = paste0(key, " (N = ", n, ")"),
    phase = factor(phase)
    ) %>% 
  select(-c(n, mean, se)) %>% 
  spread(key, mean_se) %>% 
  rename_all(.funs = ~str_to_title(.))

means_hsd <- means_aov_tukey %>% 
  select(-term) %>% 
  filter(
    comparison %in% c("control:CS+-case:CS+", "control:CS--case:CS-")
    ) %>%
  mutate_if(is.numeric, round, 2) %>% 
  mutate(
    Stimulus = case_when(
      comparison == "control:CS+-case:CS+" ~ "CS+",
      comparison == "control:CS--case:CS-" ~ "CS-",
      TRUE ~ NA_character_
    )
  )

Discriminations_hsd <- Discriminations_aov_tukey %>% 
  select(-term) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  mutate(
    Stimulus = "Discrimination"
  )

hsd_table <- bind_rows(means_hsd, Discriminations_hsd) %>% 
  mutate(
    estimate = -(estimate),
    conf.hi = -(conf.low),
    conf.lo = -(conf.high),
    Stimulus = factor(Stimulus, levels = c("CS+", "CS-", "Discrimination")),
    `HSD (95% CIs)` = paste0(estimate, " (", conf.lo, ", ", conf.hi, ")")
  ) %>% 
  select(Phase = phase, Stimulus, `HSD (95% CIs)`) %>%  
  arrange(Phase, Stimulus)

effectsize_pval <- df_cohensd %>% 
  select(Phase:Adj.p.value) %>%
  mutate(Adj.p.value = ifelse(Adj.p.value < 0.001, "< 0.001", Adj.p.value)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  mutate(`Cohen's d (95% CIs)` = paste0(Estimate, " (", Conf.int.lower, ", ", Conf.int.upper, ")")) %>% 
  select(Phase, Stimulus, `Cohen's d (95% CIs)`, `Adjusted p-value` = Adj.p.value)

expectancy_means_table <- list(expectancy_means, hsd_table, effectsize_pval) %>% reduce(left_join, by = c("Phase", "Stimulus"))

save_table(expectancy_means_table)

expectancy_means_table %>% datatable()

expectancy_means_table_gt <- expectancy_means_table %>% 
  gt(rowname_col = "Stimulus", groupname_col = "Phase") %>% 
  tab_spanner(label = "Group means (SE)", columns = contains(c("Case", "Control"))) %>% 
  cols_align(
    align = "right",
    columns = T
  ) %>% 
  tab_header(title = "Expectancy summary table")
```

## Extra
```{r}
df.long %>% 
  filter(phase == "Extinction", stimulus != "Discrimination") %>% 
  cohen.d(score ~ get(group_comparison_char), .)
```

***

# Plot {.tabset .tabset-fade}

## Barplots
```{r barplots of cohens d values, echo = FALSE, warning=FALSE}
barplots <- df_cohensd %>%
  mutate(
    Stimulus = fct_relevel(Stimulus, c("CS+", "CS-", "Discrimination"))
         ) %>% 
  # plot the cohens d estimate for each stimulus for each measure
  ggplot(data = .,
         aes(x = Stimulus, y = Estimate)
  ) +
  # add bars
  geom_bar(aes(fill = Phase),
           position = position_dodge(width = 0.9), 
           stat = "identity",
           width = .7,
           show.legend = F
  ) +
  # change colours of the bars
  scale_fill_manual(values = c("#A6BBE8", "#BDE5B0"),
                    labels = c("Acquisition", "Extinction")
  ) +
  # adjust the y axis (rename is, set limits and breaks)
  scale_y_continuous(name = "Group difference effect size (d)", 
                     limits = c(-.6, .6), 
                     breaks = round(seq(-.6,.6,.1),1)
  ) +
  # add error bars for the 95% confidence intervals, make sure the dodge is set the same as the bars
  geom_errorbar(aes(ymin = Conf.int.lower, ymax = Conf.int.upper),
                position = position_dodge(width = 0.9),
                width = 0.2
  ) +
  # wrap plots by phase (acquisition/extinction)
  facet_wrap(~ Phase) +
  # remove vertical lines, background of the phase labels (facets), the x axis title, and the legend
  theme(panel.background = element_blank(),
        panel.grid.major.y = element_line(colour = "#999999", size = 0.25),
        panel.grid.major.x = element_blank(),
        strip.text.x = element_text(size = 10),
        strip.background = element_blank(),
        panel.grid.minor = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 10),
        legend.position = "none"
  ) +
  # add title and caption
  labs(title = group_comparison_char
  ) +
  # make the x axis thicker at 0
  geom_hline(yintercept=0, 
             size = 0.5, 
             colour = "#999999"
  ) +
  # add points for duits paper estimates
  geom_point(aes(x = Stimulus, y = {{bar_diamonds}}), shape = 18, size = 3, colour = "#EF9900", alpha = 0.7) +
  # add star labels for each level of significance
  geom_text(inherit.aes = F, 
            aes(x = Stimulus, y = ynudge_001, label = "***")
  ) +
  geom_text(inherit.aes = F, 
            aes(x = Stimulus, y = ynudge_01, label = "**")
  ) +
  geom_text(inherit.aes = F, 
            aes(x = Stimulus, y = ynudge_05, label = "*")
  )

# save barplots
ggsave(
  file = paste0("../plots/",
                group_comparison_char,
                "/",
                "barplots",
                ".pdf"), 
  plot = barplots, 
  width = 30, 
  height = 20, 
  units = "cm"
  )

barplots
```

## Elephant plots {.tabset .tabset-fade}
```{r Prepare elephant data, include = FALSE}
# create a long df for trial level data to display in elephant plots
df.trial.long.grouped <- df.wide %>% 
  # select columns for each fear conditioning trial and the diagnostic group of the participants
  select({{group_comparison}}, fc_trials) %>% 
  # split the data by the diagnostic group to get a plot for each group
  group_by({{group_comparison}}) %>%
  # create a column that displays the number of participants that are in the group that the row belongs to
  mutate(., n = ifelse(get(group_comparison_char) == "case", sum(get(group_comparison_char) == "case"), sum(get(group_comparison_char) == "control"))) %>% 
  # gather to make the data long
  gather(., key, value, -c({{group_comparison}}, n)) %>% 
  # create separate columns for trial number and extra information about the phase and stimulus that the trial is associated with
  separate(., key, c("Info", "Trial"), sep = "_") %>% 
  # separate info into separate columns for phase and stimulus
  separate(., Info, c("Phase", "Stimulus"), sep = -3) %>%
  # change the trial column to a numeric column
  mutate(., Trial = as.numeric(Trial)) %>%
  ungroup() %>% 
  # group rows by their status, phase, stimulus and trial to begin making summary scores for the plot
  group_by({{group_comparison}}, Phase, Stimulus, Trial) %>%
  # create summary scores of the mean, std deviation and number of participants in each group
  summarise(mean = mean(value, na.rm = T), std.dev = sd(value, na.rm = T), n = mean(n)) %>%
  # create std error of the mean and confidence intervals
  mutate(sem = std.dev/sqrt(n),
         ci_low = mean - 2*(sem),
         ci_high = mean + 2*(sem)) %>%
  ungroup %>% 
  # reformat grouping columns to factors and sort the levels of each column out
  mutate(Phase = factor(Phase, levels = c("FCT1", "FCT3")),
         Phase = fct_recode(Phase, "Acquisition" = "FCT1", "Extinction" = "FCT3"),
         Stimulus = factor(Stimulus, levels = c("CSp", "CSm")),
         Stimulus = fct_recode(Stimulus, "CS+" = "CSp", "CS-" = "CSm")) %>%
  # arrange trials by phase, stimulus, trial
  arrange(Phase, Stimulus, Trial)


# create a long df for trial level data to display in elephant plots
df.trial.long.whole <- df.wide %>% 
  # select columns for each fear conditioning trial and the diagnostic group of the participants
  select(fc_trials) %>% 
  # create a column that displays the number of participants that are in the group that the row belongs to
  mutate(., n = nrow(.)) %>% 
  # gather to make the data long
  gather(., key, value, -n) %>% 
  # create separate columns for trial number and extra information about the phase and stimulus that the trial is associated with
  separate(., key, c("Info", "Trial"), sep = "_") %>% 
  # separate info into separate columns for phase and stimulus
  separate(., Info, c("Phase", "Stimulus"), sep = -3) %>%
  # change the trial column to a numeric column
  mutate(., Trial = as.numeric(Trial)) %>%
  # group rows by phase, stimulus and trial to begin making summary scores for the plot
  group_by(Phase, Stimulus, Trial) %>%
  # create summary scores of the mean, std deviation and number of participants
  summarise(mean = mean(value, na.rm = T), std.dev = sd(value, na.rm = T), n = mean(n)) %>%
  # create std error of the mean and confidence intervals
  mutate(sem = std.dev/sqrt(n),
         ci_low = mean - 2*(sem),
         ci_high = mean + 2*(sem)) %>%
  # ungroup
  ungroup %>% 
  # reformat grouping columns to factors and sort the levels of each column out
  mutate(Phase = factor(Phase, levels = c("FCT1", "FCT3")),
         Phase = fct_recode(Phase, "Acquisition" = "FCT1", "Extinction" = "FCT3"),
         Stimulus = factor(Stimulus, levels = c("CSp", "CSm")),
         Stimulus = fct_recode(Stimulus, "CS+" = "CSp", "CS-" = "CSm")) %>%
  # arrange trials by phase, stimulus, trial
  arrange(Phase, Stimulus, Trial)
```

### Whole elephant
```{r Whole elephant, echo=FALSE}
# create elephant plot for all participants
whole_elephant <- df.trial.long.whole %>% 
  ggplot(data = ., aes(x = Trial, y = mean, color= Stimulus)
  ) +
    # add a line to the plot
    geom_line() +
    # add error shading based on the confidence intervals
    geom_ribbon(aes(ymin = ci_low, ymax = ci_high, fill = Stimulus),
                linetype = 0,
                alpha = 0.2,
                size = .8
    ) +
    # split the plot by phase
    facet_grid(~ Phase, 
               scales = "free_x",
               space = "free_x"
    ) +
    # adjust the labels
    labs(y="Mean expectancy rating", 
         x = "Trials"
    ) +
    # remove the background and panel grids and move the legend to the bottom
    theme(strip.background = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.position = 'bottom'
    ) +
    # use the breaks_fun function to set the breaks for the x axis
    scale_x_continuous(breaks = breaks_fun) +
    # set the y axis breaks to range from minimum to maximum expectancy ratings
    scale_y_continuous(breaks = seq(0, 10, by = 1), limits = c(1, 9))

# save barplots
ggsave(
  file = paste0("../plots/",
                group_comparison_char,
                "/",
                "whole_elephant",
                ".pdf"), 
  plot = whole_elephant, 
  width = 30, 
  height = 20, 
  units = "cm"
  )

# print elephant plot for all participants
whole_elephant
```

### Grouped elephants
```{r Grouped elephants, echo=FALSE}
# create elephant plots
group_elephants <- df.trial.long.grouped %>% 
  # group the df by the different groups (e.g. case and control)
  group_by({{group_comparison}}) %>% 
  # create a plot for each of these groups with trial on the x axis and mean expectancy rating on the y axis. Group and colour the scores by stimulus type.
  group_map(~ ggplot(data = ., 
               aes(x = Trial, y = mean, color = Stimulus)
  ) +
    # add a line to the plot
    geom_line() +
    # add error shading based on the confidence intervals
    geom_ribbon(aes(ymin = ci_low, ymax = ci_high, fill = Stimulus),
                linetype = 0,
                alpha = 0.2,
                size = .8
    ) +
    # split the plot by phase
    facet_grid(. ~ Phase, 
               scales = "free_x",
               space = "free_x"
    ) +
    # adjust the labels
    labs(y="Mean expectancy rating", 
         x = "Trials",
         # adjust the title based on the status of the participants used
         title = unique(.[ , group_comparison_char])
    ) +
    # remove the background and panel grids and move the legend to the bottom
    theme(strip.background = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.position = 'bottom'
    ) +
    # use the breaks_fun function to set the breaks for the x axis
    scale_x_continuous(breaks = breaks_fun) +
    # set the y axis breaks to range from minimum to maximum expectancy ratings
    scale_y_continuous(breaks = seq(0, 10, by = 1), limits = c(1, 9)),
  keep = T
  )

# print all of the plots held in the list of elephant plots that were created
for (i in 1:length(group_elephants)) {
    print(group_elephants[[i]])
}
```